Modelling the Lymphatic Metastatic Progression Pathways of OPSCC from Multi-Institutional Datasets

### 2022-12-21 src/tex/ms.tex
[showyourwork] overleaf sync

>>>>

\begin{figure}
    \script{comp_IandII_low_prevs.py}
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/comp_IandII_low_prevs.png}
        \caption{This should be a one-column wide figure.}
        \label{fig:IandII_low_prevs}
    \end{centering}
\end{figure}

\begin{figure}
    \script{comp_IandII_high_prevs.py}
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/comp_IandII_high_prevs.png}
        \caption{This should be a one-column wide figure.}
        \label{fig:IandII_high_prevs}
    \end{centering}
\end{figure}

\section{Results}
\label{sec:results}

\begin{center}
    \begin{tabular}{|l|l|l|l|}
        \hline
        \textbf{Graph} & \textbf{-- BIC/2} & \textbf{max. llh} & \textbf{mean llh} \\
        \hline
        base graph    & \variable{output/bg_BIC.txt} & \variable{output/bg_max_llh.txt} & \variable{output/bg_mean_llh.txt} \\
        winning graph & \variable{output/wg_BIC.txt} & \variable{output/wg_max_llh.txt} & \variable{output/wg_mean_llh.txt} \\
        \hline
    \end{tabular}
\end{center}
